---
title: "Group_14_Exam"
format: html
editor: visual
---

*This exam project has been conducted by group 14 which includes the students:*

| Name                      | Student number |
|---------------------------|----------------|
| Caroline Sofie Hermannsen | s215016        |
| Helene Nielsen            | s215037        |
| Kathrine                  | s215052        |
| Nadia                     | s215055        |

*All group members contributed equally.*

## Background

What we do: See google docs document: <https://docs.google.com/document/d/1yNVCNuAO6bL3kIM9ScEc9Kdcnw6VaJup2c3B_c9R7Nk/edit?usp=sharing>

Coral reefs around the world are experiencing increased stress due to rising sea-surface temperatures and other climate-driven changes. Coral bleaching is the loss of symbiotic algae from coral tissues, which is often precipitated by thermal stress. It is one of the most visible and damaging consequences of these shifts. The study by Sully et al. addresses how bleaching patterns have varied globally over recent decades.

Using field observations collected at 3,351 reef sites across 81 countries between 1998 and 2017, the authors combined these bleaching records with environmental and temperature metrics to identify spatial and temporal patterns.

Here we want to perform Data Wrangling and Data Analysis on the datasets from the study. The datasets used are described in Data Description below.

## Data Description

## Aim

## Load Libraries

```{r}
#| message: false
library("tidyverse")
```

## Load Data

The two different datasets are here loaded into the document and saved as data1 and data2. When viewing the two files, we see that they both contain ReefID_Name as the first column. This column is untidy since we have two different informations in one cell.

```{r}
#| message: false
data1 <- read_csv(file="data/_raw/reef_data_dataset1.csv")
data2 <- read_csv(file="data/_raw/reef_data_dataset2.csv")

View(data1)
View(data2)
```

## Data Wrangling

Starting out with the data wrangling we want to first combine the two datasets using the join function and combining them by their common column.

```{r}
#| message: false
reef_combined_untidy <- data1 |>
  left_join(data2, by = "ReefID_Name")

write_csv(reef_combined_untidy, "data/_raw/reef_data_combined_untidy.csv")
```

Now we want to tidy the dataset, and turn ReefID_Name into two separate variables. For this we use the seperate function and split them by "\|".

```{r}
reef_combined_tidy <- reef_combined_untidy |>
  separate(
    col  = "ReefID_Name",
    into = c("Reef.ID", "Reef.Name"),
    sep  = " \\| "
  ) |>
  relocate(Reef.ID, Reef.Name, .before = 1)

View(reef_combined_tidy)

write_csv(reef_combined_tidy, "data/_raw/reef_data_combined_tidy.csv")
```

## Data Analysis

## Conclusion
