---
title: "Group_14_Exam"
format: html
editor: visual
---

*This exam project has been conducted by group 14 which includes the students:*

| Name                      | Student number |
|---------------------------|----------------|
| Caroline Sofie Hermannsen | s215016        |
| Helene Nielsen            | s215037        |
| Kathrine                  | s              |
| Nadia                     | s              |

All group members contributed equally.


## Background

What we do:

Tidy:

-   Splitting columns

-   Adding variables

-   

-   What is this project about

-   Describe what data files are the original ones and which one we untidied

-   Another point

## Aim

Hej jeg hedder Nadia

## Load Libraries

```{r}
#| message: false
library("tidyverse")
#library("here")
```

## Load Data

```{r}
#| message: false
untidy_data <- read_csv(file="data/_raw/Reef_Check_Data_Untidy.csv")
```

## Data Description


## Analysis

Tidy data:

-   Untidy names separate columns
<<<<<<< HEAD

Analyze data:


-   Make graphs over reefh


-   Make graphs over reefh
>>>>>>> fa6f9cf5f97dc1b7269dfd4a8a6036314c6083d5
=======

>>>>>>> d735a0f701d85ebe816c1b81eee3b389ba5c31b7


>>>>>>> 234ecb94be146dbdce8439f9de7c88cb3f20b6b5
