---
title: "Group_14_Exam"
format: html
editor: visual
---

*This exam project has been conducted by group 14 which includes the students:*

| Name                      | Student number |
|---------------------------|----------------|
| Caroline Sofie Hermannsen | s215016        |
| Helene Nielsen            | s215037        |
| Kathrine                  | s215052        |
| Nadia                     | s215055        |

*All group members contributed equally.*

## Background

What we do: See google docs document: <https://docs.google.com/document/d/1yNVCNuAO6bL3kIM9ScEc9Kdcnw6VaJup2c3B_c9R7Nk/edit?usp=sharing>

-   What is this project about

-   Describe what data files are the original ones and which one we untidied

-   Another point

## Aim

## Load Libraries

```{r}
#| message: false
library("tidyverse")
```

## Load Data

```{r}
#| message: false
data1 <- read_csv(file="data/_raw/reef_data_dataset1.csv")
data2 <- read_csv(file="data/_raw/reef_data_dataset2.csv")
```

## Data Description

## Data Wrangling

Now we join the datasets using the untidy combined dataset.

```{r}
#| message: false
reef_combined_untidy <- data1 |>
  left_join(data2, by = "ReefID_Name")

# Save the untidy version
write_csv(reef_combined_untidy, "data/_raw/reef_data_combined_untidy.csv")
```

We tidy the combined column, ReefID_Name into two separate variables.

```{r}
reef_combined_tidy <- reef_combined_untidy |>
  separate(
    col  = "ReefID_Name",
    into = c("Reef.ID", "Reef.Name"),
    sep  = " \\| "
  ) |>
  relocate(Reef.ID, Reef.Name, .before = 1)

# Look at the final tidy dataset
View(reef_combined_tidy)

# Save the tidy version
write_csv(reef_combined_tidy, "data/_raw/reef_data_combined_tidy.csv")
```

## Data Analysis
