---
title: "Group_14_Exam"
format: html
editor: visual
---

*This exam project has been conducted by group 14 that includes the students:*

| Name                      | Student number |
|---------------------------|----------------|
| Caroline Sofie Hermannsen | s215016        |
| Helene Nielsen            | s215037        |
| Nadia                     | s              |
| Kathrine                  | s              |

-   Caroline Sofie Hermannsen - s215016

-   Helene Nielsen - s215037

-   x

-   x

All group members contributed equally.

## Background

What we do:

Tidy:

-   Splitting columns

-   Adding variables

-   

-   What is this project about

-   Describe what data files are the original ones and which one we untidied

-   Another point

## Aim

Hej jeg hedder Nadia

## Load Libraries

```{r}
#| message: false
library("tidyverse")
#library("here")
```

## Load Data

```{r}
#| message: false
untidy_data <- read_csv(file="data/_raw/Reef_Check_Data_Untidy.csv")
```

## Data Description

<<<<<<< HEAD
## Analysis
=======
Tidy data:

-   Untidy names separate columns

Analyze data:

<<<<<<< HEAD
<<<<<<< HEAD
-   Make graphs over reefh
>>>>>>> fa6f9cf5f97dc1b7269dfd4a8a6036314c6083d5
=======


## 
